---
title: "Calibrate SOFUN"
author: "Benjamin D. Stocker"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
# output:
#   pdf_document:
#     toc: true
#     toc_depth: 2
header-includes:
   - \usepackage{amsmath}
# bibliography: bibliography.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(captioner)
library(rsofun)
load_dependencies_rsofun()
tab_nums <- captioner( prefix = "Table S", auto_space=FALSE, style = "i" )
fig_nums <- captioner( prefix = "Figure S", auto_space=FALSE, style = "i" )
systr <- "''"    # for Mac
```

## Calibration settings

First, load simulation and input settings defined outside (e.g. as shown in `vignette_rsofun.Rmd`).
```{r message=FALSE}
library(dplyr)
library(readr)
library(rsofun)
source("filter_days.R")

settings_sims <- list(
  path_siteinfo   = "./ext/siteinfo_fluxnet2015.csv",
  ensemble        = TRUE,
  setup           = "site",
  name            = "fluxnet2015",
  dir_sofun       = "~/sofun/trunk/",
  path_output     = "~/sofun/output_fluxnet2015_sofun/s24/",
  path_output_nc  = "~/sofun/output_nc_fluxnet2015_sofun/s24/",
  path_input      = "~/sofun/input_fluxnet2015_sofun_TEST/",
  grid            = NA,
  implementation  = "fortran",
  in_ppfd         = TRUE,
  in_netrad       = FALSE,
  recycle         = 1,
  spinupyears     = 10,
  calibvars       = c("gpp"),
  soilmstress     = TRUE,
  tempstress      = TRUE,
  loutdgpp        = TRUE,
  loutdwcont      = TRUE,
  loutdaet        = TRUE,
  loutdpet        = TRUE,
  loutdalpha      = TRUE
  )

settings_input <-  list(
  data                     = NA,
  temperature              = "fluxnet2015",
  precipitation            = "fluxnet2015",
  vpd                      = "fluxnet2015",
  ppfd                     = "fluxnet2015",
  netrad                   = NA,
  cloudcover               = "cru",
  path_watch_wfdei         = "~/data/watch_wfdei/",
  path_cru                 = "~/data/cru/ts_4.01/",
  path_MODIS_EVI_MOD13Q1   = "~/data/fapar_MODIS_EVI_MOD13Q1_gee_MOD13Q1_fluxnet2015_gee_subset/",
  path_MODIS_FPAR_MCD15A3H = "~/data/fapar_MODIS_FPAR_MCD15A3H_gee_MCD15A3H_fluxnet2015_gee_subset/",
  path_co2                 = "~/data/co2/cCO2_rcp85_const850-1765.dat",
  path_fluxnet2015         = "~/data/FLUXNET-2015_Tier1/20160128/point-scale_none_1d/original/unpacked/",
  get_from_remote          = FALSE
  )

setup_sofun <- list(
  model      = "pmodel",
  dir        = "~/sofun/trunk",
  do_compile = FALSE,
  simsuite   = FALSE
  )
```

Then define the calibration settings as.
```{r}
## Use only sites for calibration for which ANN method by Stocker et al. (2018) worked fine,
## and exclude sites where C4 vegetation is present.
siteinfo <- read_csv( settings_sims$path_siteinfo )
calibsites <- readr::read_csv( "~/data/flue/flue_stocker18nphyt.csv" ) %>%
              dplyr::filter( !is.na(cluster) ) %>%
              dplyr::select( site ) %>%
              distinct() %>%

              ## additionally exclude C4
              dplyr::filter( !(site %in% dplyr::filter(siteinfo, c4 )$mysitename) ) %>%

              dplyr::select( site ) %>%
              unlist()

# ## Calibration sites test ("5sites")
# calibsites <- c("AU-Tum", "FR-Pue", "IT-Cpz", "FI-Hyy", "NL-Loo" )

# ## Calibration sites for TerraP, excluding CA-Obs
# calibsites <- c("AU-Tum", "CA-NS3", "CA-NS6", "DE-Geb", "DE-Hai", "DE-Kli", "FI-Hyy", "FR-Fon", "FR-LBr", "FR-Pue", "IT-Cpz", "NL-Loo", "US-Ha1", "US-MMS", "US-UMB", "US-WCr")

## Define calibration settings common for all setups
settings_calib <- list(
  method           = "gensa",
  targetvars       = c("gpp"),
  timescale        = list( gpp = "d" ),
  path_fluxnet2015 = "~/data/FLUXNET-2015_Tier1/20160128/point-scale_none_1d/original/unpacked/",
  path_gepisat     = "~/data/gepisat/v3_fluxnet2015/daily_gpp/",
  maxit            = 10, # (5 for gensa) (30 for optimr)    #
  sitenames        = calibsites,  # dplyr::filter(siteinfo$light, c4 %in% c(FALSE, NA) )$mysitename, # calibrate for non-C4 sites
  filter_temp_max  = 35.0,
  filter_drought   = FALSE,
  metric           = "rmse",
  dir_results      = "/Users/benjaminstocker/eval_pmodel/calib_results"
 )
```

- `name`: A character string to define a name used for this calibration, used in file names containing calibration outputs.
- `par`: list of parameters to calibrate with their lower and upper boundaries. This is rigid. If you chose to use different parameters or in a different order, modify code in `calib_sofun.R` (function `cost_rmse()`) and in the model source code (`sofun/src/sofun.f90`).
- `targetvars`: Character string for name of variable in SOFUN output
- `datasource`: Named list of character strings with data source identifiers for each calibration target variable. The list is named corresponding to variable names defined by 'targetvars'. The identifier triggers certain functions to be used for reading and processing observational data. Use, e.g., `datasource = list( gpp = "fluxnet2015_NT" )` to specify that observational data for the target variable `"gpp"` comes from FLUXNET 2015 dataset with GPP data based on the night-time flux decomposition method (`"NT"`). Alternatively, use GPP data based on the daytime method (`"fluxnet2015_NT"`) or Tyler Davis' new method (unpublished) (`"fluxnet2015_Ty"`). If multiple data sources are selected (e.g., `datasource = list( gpp = c("fluxnet2015_NT", "fluxnet2015_DT") )`), their mean is used for calibration.
- `timescale`: Named list of characters specifying the time scale used for aggregating modelled and observational data in time series before calculating the cost function. For naming the list, see point above. Set, e.g., `timescale = list( gpp = "d" )` to calibrate to observational GPP aggregated to daily intervals (i.e. not aggregated). Use `"w"` for weekly, `"m"` for monthly, or `"y"` for annual (XXX NOT YET IMPLEMENTED).
- `path_fluxnet2015`: Path (character string) for where FLUXNET 2015 data is located (data files may be in subdirectories thereof). This settings list element needs to be specified if any of `datasource` is `"fluxnet2015"`.
- `path_gepisat`: Path (character string) for where GePiSaT GPP data is located (data files may be in subdirectories thereof). This settings list element needs to be specified if any of `datasource` is `"gepisat"`.
- `sitenames`: Vector of character strings for site names of sites' data to be used for calibration.
- `filter_temp_min`: Minimum temperature of data used for calibration. Data points for days where air temperature is below, are removed (replaced by NA) in the observational data.
- `filter_temp_max`: Maximum temperature of data used for calibration. Data points for days where air temperature is above, are removed (replaced by NA) in the observational data.
- `filter_soilm_min`: Minimum soil moisture (relative, normalised to maximum of mean across multiple depths at each site) of data used for calibration. Data points for days where soil moisture is below, are removed (replaced by NA) in the observational data.
- `metric`: A character string specifying the metric to be used for calulating the cost.


## Calibration of different simulation suites

Parameters are calibrated for six different simulation suites and parameter values saved in CSV files. The simulation suites are FLUXNET site-scale simulations with different fAPAR input data, differrent GPP calibration target data, and different model setups (empirical soil moisture and temperature stress function) with their calibration data set. 

| Output set    | fAPAR data                       | GPP target data | Calibration set  | SM limit.  | temp stress | setup name   | parameter file name                 |
|---------------|----------------------------------|---------------- |----------------- |------------|-------------|--------------|----------------------------------   |
| s24           | MODIS FPAR MCD15A3H, splined     | NT              | valid NT data    | no         | no          | ORG          | params_opt_calib_ORG.csv            |
| s30           | MODIS FPAR MCD15A3H, splined     | NT              | valid NT data    | no         | yes         | BRC          | params_opt_calib_BRC.csv            |
| s25           | MODIS FPAR MCD15A3H, splined     | NT              | valid NT data    | yes        | yes         | FULL         | params_opt_calib_FULL.csv           |
|---------------|----------------------------------|---------------- |----------------- |------------|-------------|--------------|----------------------------------   |
| s26           | MODIS FPAR MCD15A3H, interpolated| NT              | valid NT data    | yes        | yes         | FULL_FPARitp | params_opt_calib_FULL_FPARitp.csv   |
| s27           | MODIS EVI MOD13Q1, interpolated  | NT              | valid NT data    | yes        | yes         | FULL_EVI     | params_opt_calib_FULL_EVI.csv       |
|---------------|----------------------------------|---------------- |----------------- |------------|-------------|--------------|----------------------------------   |
| s28           | MODIS FPAR MCD15A3H, splined     | DT              | valid NT, DT, Ty | yes        | yes         | FULL_DT      | params_opt_calib_FULL_DT.csv        |
| s29           | MODIS FPAR MCD15A3H, splined     | Ty              | valid NT, DT, Ty | yes        | yes         | FULL_Ty      | params_opt_calib_FULL_Ty.csv        |
| s31           | MODIS FPAR MCD15A3H, splined     | NT              | valid NT, DT, Ty | yes        | yes         | FULL_NTsub   | params_opt_calib_FULL_DT.csv        |
|---------------|----------------------------------|---------------- |----------------- |------------|-------------|--------------|----------------------------------   |


### Setup `ORG`

Define settings, prepare setup and input data and do the calibration for the setup `ORG`. This calibrates only `kphio`. `settings_calib()` returns calibration settings, now including calibrated parameters inside the list (`settings_calib$par[[param_name]]$opt`). Calibrated parameters are also written to a CSV file `"params_opt_ORG.csv"`.

```{r, eval=FALSE, message=FALSE, warning=FALSE}
## Define calibration setup-specific simulation parameters
settings_sims$soilmstress = FALSE
settings_sims$tempstress  = FALSE
settings_sims$loutdgpp    = FALSE
settings_sims$loutdrd     = FALSE
settings_sims$loutdtransp = FALSE
settings_sims$loutdwcont  = FALSE
settings_sims$loutdaet    = FALSE
settings_sims$loutdpet    = FALSE
settings_sims$loutdalpha  = FALSE

## Prepare the model setup for this calibration set
settings_sims <- prepare_setup_sofun( 
  settings = settings_sims, 
  write_paramfils = TRUE 
  )

## Define fAPAR input data and re-write input files for SOFUN
settings_input$fapar = "MODIS_FPAR_MCD15A3H"
settings_input$splined_fapar = TRUE

inputdata <- prepare_input_sofun( 
  settings_input = settings_input, 
  settings_sims = settings_sims, 
  return_data = FALSE, 
  overwrite_csv_fapar = FALSE, 
  overwrite_fapar = FALSE, 
  verbose = TRUE
  )

## Additional setup-specific calibration-settings
## Specify data source for observations to which model is calibrated
settings_calib_ORG <- settings_calib
settings_calib_ORG$name = "ORG"
settings_calib_ORG$par = list( kphio = list( lower=0.01, upper=0.12, init=0.05 ) )
settings_calib_ORG$datasource = list( gpp = "fluxnet2015_NT" )
settings_calib_ORG$filter_temp_min = NA
settings_calib_ORG$filter_soilm_min = NA

## Get observational data (GPP based on NT method) used as target for calibration
if (!exists("ddf_obs_NT")){
  ddf_obs_NT <- get_obs_calib( settings_calib_ORG, settings_sims, settings_input )
  save( ddf_obs_NT, file = "./data/ddf_obs_NT.Rdata" )
}

settings_calib_ORG <- calib_sofun(
  setup          = setup_sofun,
  settings_calib = settings_calib_ORG,
  settings_sims  = settings_sims,
  settings_input = settings_input,
  ddf_obs        = ddf_obs_NT
  )
```


### Setup `BRC`

The setup `BRC` is different from `ORG` in that it implements the temperature dependence of the quantum yield efficiency parameter after Bernacchi et al., 2003 PCE (included by setting `settings_sims$tempstress  = TRUE`)

```{r, eval=FALSE, message=FALSE, warning=FALSE}
## Define calibration setup-specific simulation parameters
settings_sims$soilmstress = FALSE
settings_sims$tempstress  = TRUE

## Prepare the model setup for this calibration set
settings_sims <- prepare_setup_sofun( 
  settings = settings_sims, 
  write_paramfils = TRUE 
  )

## Define fAPAR input data and re-write input files for SOFUN
settings_input$fapar = "MODIS_FPAR_MCD15A3H"
settings_input$splined_fapar = TRUE

inputdata <- prepare_input_sofun( 
  settings_input = settings_input, 
  settings_sims = settings_sims, 
  return_data = FALSE, 
  overwrite_csv_fapar = FALSE, 
  overwrite_fapar = FALSE, 
  verbose = TRUE
  )

## Additional setup-specific calibration-settings
## Specify data source for observations to which model is calibrated
settings_calib_BRC <- settings_calib
settings_calib_BRC$name = "BRC"
settings_calib_BRC$par = list( kphio = list( lower=0.01, upper=0.2, init=0.05 ) )
settings_calib_BRC$datasource = list( gpp = "fluxnet2015_NT" )
settings_calib_BRC$filter_temp_min = NA
settings_calib_BRC$filter_soilm_min = NA

## Get observational data (GPP based on NT method) used as target for calibration
if (!exists("ddf_obs_NT")){
  ddf_obs_NT <- get_obs_calib( settings_calib_BRC, settings_sims, settings_input )
  save( ddf_obs_NT, file = "./data/ddf_obs_NT.Rdata" )
}

settings_calib_BRC <- calib_sofun(
  setup          = setup_sofun,
  settings_calib = settings_calib_BRC,
  settings_sims  = settings_sims,
  settings_input = settings_input,
  ddf_obs        = ddf_obs_NT
  )
```


### Setup `FULL`

Define settings, prepare setup and input data and do the calibration for the setup `FULL`. This is based on all data (including dry and cold days), with empirical soil moisture and low temperature stress functions and calibrates multiple parameters at once (`kphio` and parameters related to the soil moisture and temperature stress functions.

```{r, eval=FALSE, message=FALSE, warning=FALSE}
## Define calibration setup-specific simulation parameters
settings_sims$soilmstress = TRUE
settings_sims$tempstress  = TRUE

## Prepare the model setup for this calibration set
settings_sims <- prepare_setup_sofun( 
  settings = settings_sims, 
  write_paramfils = FALSE 
  )

## Same fAPAR data used as above - nothing to be done 
## Define fAPAR input data and re-write input files for SOFUN
settings_input$fapar = "MODIS_FPAR_MCD15A3H"
settings_input$splined_fapar = TRUE

inputdata <- prepare_input_sofun(
  settings_input = settings_input,
  settings_sims = settings_sims,
  return_data = FALSE,
  overwrite_csv_fapar = FALSE, # WARNING: ASSUMING "LINEAR" KNITTING 
  overwrite_fapar = FALSE, # WARNING: ASSUMING "LINEAR" KNITTING 
  verbose = TRUE
  )

## Additional setup-specific calibration-settings
## Specify data source for observations to which model is calibrated
settings_calib_FULL <- settings_calib
settings_calib_FULL$name = "FULL"
settings_calib_FULL$par = list( kphio          = list( lower=0.01, upper=0.4, init=0.1 ),
                                soilm_par_a    = list( lower=0.0, upper=1.0, init=0.2 ),
                                soilm_par_b    = list( lower=0.0, upper=2.0, init=0.2 ) )
settings_calib_FULL$datasource = list( gpp = "fluxnet2015_NT" )
settings_calib_FULL$filter_temp_min = NA
settings_calib_FULL$filter_soilm_min = NA

## load obs data if not available
if (!exists("ddf_obs_NT")) load("./data/ddf_obs_NT.Rdata")

## Same observational data as for setup 'RED' (filtering is done afterwards, inside calib_sofun())
settings_calib_FULL <- calib_sofun(
  setup          = setup_sofun,
  settings_calib = settings_calib_FULL,
  settings_sims  = settings_sims,
  settings_input = settings_input,
  ddf_obs        = ddf_obs_NT
  )
```

<!-- #### Additional test for `FULL`
Test the sensitivity of calibrated parameters to the observational data: repeat calibration of each site separately.
```{r}
# ## test 
# settings_calib_FULL_1site <- calib_sofun(
#   setup          = setup_sofun,
#   settings_calib = settings_calib_FULL,
#   settings_sims  = settings_sims,
#   settings_input = settings_input,
#   ddf_obs        = dplyr::filter( ddf_obs_NT, sitename=="FR-Pue" ),
#   sitename       = "FR-Pue"
#   )

# list_calib_bysite <- purrr::map( as.list(calibsites), 
#                                  ~calib_sofun(
#                                               setup          = setup_sofun,
#                                               settings_calib = settings_calib_FULL,
#                                               settings_sims  = settings_sims,
#                                               settings_input = settings_input,
#                                               ddf_obs        = dplyr::filter( ddf_obs_NT, sitename==. ),
#                                               sitename       = .
#                                               ) )
# save( list_calib_bysite, file = "data/list_calib_bysite.Rdata" )
```
 -->

### Sensitivity to fAPAR forcing data with `FULL_FPARitp` and `FULL_EVI`

Do the same as described under `FULL`, but with alternative fAPAR data. Calibrated parameters are written to `"params_opt_FULL_FPARitp.csv"` and `"params_opt_FULL_EVI.csv"`.

#### Setup `FULL_FPARitp`
```{r, eval=FALSE, message=FALSE, warning=FALSE}
## Define calibration setup-specific simulation parameters
settings_sims$soilmstress = TRUE
settings_sims$tempstress  = TRUE

## Prepare the model setup for this calibration set
settings_sims <- prepare_setup_sofun( 
  settings = settings_sims, 
  write_paramfils = FALSE 
  )

## Define fAPAR input data and re-write input files for SOFUN
settings_input$fapar = "MODIS_FPAR_MCD15A3H"
settings_input$splined_fapar = FALSE

inputdata <- prepare_input_sofun( 
  settings_input = settings_input, 
  settings_sims = settings_sims, 
  return_data = FALSE, 
  overwrite_csv_fapar = FALSE,
  overwrite_fapar = FALSE,
  verbose = TRUE
  )

## Additional setup-specific calibration-settings
## Specify data source for observations to which model is calibrated
settings_calib_FULL_FPARitp <- settings_calib
settings_calib_FULL_FPARitp$name = "FULL_FPARitp"
settings_calib_FULL_FPARitp$par = list( kphio       = list( lower=0.01, upper=0.4, init=0.1 ),
                                        soilm_par_a = list( lower=0.0, upper=1.0, init=0.2 ),
                                        soilm_par_b = list( lower=0.0, upper=2.0, init=0.2 ) )
settings_calib_FULL_FPARitp$datasource = list( gpp = "fluxnet2015_NT" )
settings_calib_FULL_FPARitp$filter_temp_min = NA
settings_calib_FULL_FPARitp$filter_soilm_min = NA

settings_calib_FULL_FPARitp <- calib_sofun(
  setup          = setup_sofun,
  settings_calib = settings_calib_FULL_FPARitp,
  settings_sims  = settings_sims,
  settings_input = settings_input,
  ddf_obs        = ddf_obs_NT
  )
```


#### Setup `FULL_EVI`
```{r, eval=FALSE, message=FALSE, warning=FALSE}
## Define calibration setup-specific simulation parameters
settings_sims$soilmstress = TRUE
settings_sims$tempstress  = TRUE

## Prepare the model setup for this calibration set
settings_sims <- prepare_setup_sofun( 
  settings = settings_sims, 
  write_paramfils = FALSE 
  )
## Define fAPAR input data and re-write input files for SOFUN
settings_input$fapar = "MODIS_EVI_MOD13Q1"
settings_input$splined_fapar = FALSE

inputdata <- prepare_input_sofun( 
  settings_input = settings_input, 
  settings_sims = settings_sims, 
  return_data = FALSE, 
  overwrite_csv_fapar = FALSE,
  overwrite_fapar = FALSE,
  verbose = TRUE
  )

## Additional setup-specific calibration-settings
## Specify data source for observations to which model is calibrated
settings_calib_FULL_EVI <- settings_calib
settings_calib_FULL_EVI$name = "FULL_EVI"
settings_calib_FULL_EVI$par = list( kphio       = list( lower=0.01, upper=0.4, init=0.1 ),
                                    soilm_par_a = list( lower=0.0, upper=1.0, init=0.2 ),
                                    soilm_par_b = list( lower=0.0, upper=2.0, init=0.2 ) )
settings_calib_FULL_EVI$datasource = list( gpp = "fluxnet2015_NT" )
settings_calib_FULL_EVI$filter_temp_min = NA
settings_calib_FULL_EVI$filter_soilm_min = NA

settings_calib_FULL_EVI <- calib_sofun(
  setup          = setup_sofun,
  settings_calib = settings_calib_FULL_EVI,
  settings_sims  = settings_sims,
  settings_input = settings_input,
  ddf_obs        = ddf_obs_NT
  )
```


### Sensitivity to target GPP data with `FULL_DT` and `FULL_Ty` and `FULL_NTsub`

Do the same as described under `ORG`, but with alternative calibration target data: GPP based on the daytime decomposition method and GPP on GePiSaT method. Note that GPP data decomposed based on the GePiSaT method is much sparser than the FLUXNET 2015 data (NT and DT decomposition). To have a fair comparison, we use days that have valid data in all datasets GePiSaT, NT, and DT. This requires the `FULL` setup to be repeated with only a subset of the data (`FULL_NTsub`). Calibrated parameters are written to `"params_opt_FULL_DT.csv"` and `"params_opt_FULL_Ty.csv"`.

#### Setup `FULL_DT`

```{r, eval=FALSE, message=FALSE, warning=FALSE}
## Define calibration setup-specific simulation parameters
settings_sims$soilmstress = TRUE
settings_sims$tempstress  = TRUE

## Prepare the model setup for this calibration set
settings_sims <- prepare_setup_sofun( 
  settings = settings_sims, 
  write_paramfils = FALSE 
  )

## Define fAPAR input data and re-write input files for SOFUN
settings_input$fapar = "MODIS_FPAR_MCD15A3H"
settings_input$splined_fapar = TRUE

inputdata <- prepare_input_sofun( 
  settings_input = settings_input, 
  settings_sims = settings_sims, 
  return_data = FALSE, 
  overwrite_csv_fapar = FALSE, 
  overwrite_fapar = FALSE, 
  verbose = TRUE
  )

## Additional setup-specific calibration-settings
## Specify data source for observations to which model is calibrated
settings_calib_FULL_DT <- settings_calib
settings_calib_FULL_DT$name <- "FULL_DT"
settings_calib_FULL_DT$par <- list( kphio          = list( lower=0.01, upper=0.4, init=0.1 ),
                                    soilm_par_a    = list( lower=0.0, upper=1.0, init=0.2 ),
                                    soilm_par_b    = list( lower=0.0, upper=2.0, init=0.2 ) )
settings_calib_FULL_DT$datasource = list( gpp = "fluxnet2015_DT" )
settings_calib_FULL_DT$filter_days = c("fluxnet2015_Ty", "fluxnet2015_DT", "fluxnet2015_NT")
settings_calib_FULL_DT$filter_temp_min = NA
settings_calib_FULL_DT$filter_soilm_min = NA

## Get observational data (GPP based on NT method) used as target for calibration
if (!exists("ddf_obs_DTsub")){
  ddf_obs_DTsub <- get_obs_calib( settings_calib_FULL_DT, settings_sims, settings_input )
  ddf_obs_DTsub <- ddf_obs_DTsub %>% filter_days( settings_calib_FULL_DT$filter_days, settings_calib_FULL_DT$path_gepisat )
  save(ddf_obs_DTsub, file = "data/ddf_obs_DTsub.Rdata")
} else {
  load("data/ddf_obs_DTsub.Rdata")
}
print(paste0("Total number of calibration target data points: ", sum(!is.na(ddf_obs_DTsub$gpp_obs))))

settings_calib_FULL_DT <- calib_sofun(
  setup          = setup_sofun,
  settings_calib = settings_calib_FULL_DT,
  settings_sims  = settings_sims,
  settings_input = settings_input,
  ddf_obs        = ddf_obs_DTsub
  )
```

#### Setup `FULL_NTsub`

```{r, eval=TRUE, message=FALSE, warning=FALSE}
## Define calibration setup-specific simulation parameters
settings_sims$soilmstress = TRUE
settings_sims$tempstress  = TRUE

## Prepare the model setup for this calibration set
settings_sims <- prepare_setup_sofun( 
  settings = settings_sims, 
  write_paramfils = FALSE 
  )

## Define fAPAR input data and re-write input files for SOFUN
settings_input$fapar = "MODIS_FPAR_MCD15A3H"
settings_input$splined_fapar = TRUE

inputdata <- prepare_input_sofun( 
  settings_input = settings_input, 
  settings_sims = settings_sims, 
  return_data = FALSE, 
  overwrite_csv_fapar = FALSE, 
  overwrite_fapar = FALSE, 
  verbose = TRUE
  )

## Additional setup-specific calibration-settings
## Specify data source for observations to which model is calibrated
settings_calib_FULL_NTsub <- settings_calib
settings_calib_FULL_NTsub$name <- "FULL_NTsub"
settings_calib_FULL_NTsub$par <- list(  kphio          = list( lower=0.01, upper=0.4, init=0.1 ),
                                        soilm_par_a    = list( lower=0.0, upper=1.0, init=0.2 ),
                                        soilm_par_b    = list( lower=0.0, upper=2.0, init=0.2 ) )
settings_calib_FULL_NTsub$datasource = list( gpp = "fluxnet2015_NT" )
settings_calib_FULL_NTsub$filter_days = c("fluxnet2015_Ty", "fluxnet2015_DT", "fluxnet2015_NT")
settings_calib_FULL_NTsub$filter_temp_min = NA
settings_calib_FULL_NTsub$filter_soilm_min = NA

## Get observational data (GPP based on NT method) used as target for calibration
if (!exists("ddf_obs_NTsub")){
  ddf_obs_NTsub <- get_obs_calib( settings_calib_FULL_NTsub, settings_sims, settings_input )
  ddf_obs_NTsub <- ddf_obs_NTsub %>% filter_days( settings_calib_FULL_NTsub$filter_days, settings_calib_FULL_NTsub$path_gepisat )
  save( ddf_obs_NTsub, file = "data/ddf_obs_NTsub.Rdata")
} else {
  load("data/ddf_obs_NTsub.Rdata")
}
print(paste0("Total number of calibration target data points: ", sum(!is.na(ddf_obs_NTsub$gpp_obs))))

settings_calib_FULL_NTsub <- calib_sofun(
  setup          = setup_sofun,
  settings_calib = settings_calib_FULL_NTsub,
  settings_sims  = settings_sims,
  settings_input = settings_input,
  ddf_obs        = ddf_obs_NTsub
  )
```


#### Setup `FULL_Ty`

```{r, eval=TRUE, message=FALSE, warning=FALSE}
## Define calibration setup-specific simulation parameters
settings_sims$soilmstress = TRUE
settings_sims$tempstress  = TRUE

## Prepare the model setup for this calibration set
settings_sims <- prepare_setup_sofun( 
  settings = settings_sims, 
  write_paramfils = FALSE 
  )

## Define fAPAR input data and re-write input files for SOFUN
settings_input$fapar = "MODIS_FPAR_MCD15A3H"
settings_input$splined_fapar = TRUE

inputdata <- prepare_input_sofun( 
  settings_input = settings_input, 
  settings_sims = settings_sims, 
  return_data = FALSE, 
  overwrite_climate = FALSE, 
  overwrite_csv_fapar = FALSE, 
  overwrite_fapar = FALSE, 
  verbose = TRUE
  )

## Additional setup-specific calibration-settings
## Specify data source for observations to which model is calibrated
settings_calib_FULL_Ty <- settings_calib
settings_calib_FULL_Ty$name = "FULL_Ty"
settings_calib_FULL_Ty$par = list( kphio          = list( lower=0.01, upper=0.4, init=0.1 ),
                                   soilm_par_a    = list( lower=0.0, upper=1.0, init=0.2 ),
                                   soilm_par_b    = list( lower=0.0, upper=2.0, init=0.2 ) )
settings_calib_FULL_Ty$datasource = list( gpp = "fluxnet2015_Ty" )
settings_calib_FULL_Ty$filter_days = c("fluxnet2015_Ty", "fluxnet2015_DT", "fluxnet2015_NT")
settings_calib_FULL_Ty$filter_temp_min = NA
settings_calib_FULL_Ty$filter_soilm_min = NA

## Get observational data (GPP based on NT method) used as target for calibration
if (!exists("ddf_obs_Ty")){
  ddf_obs_Ty <- get_obs_calib( settings_calib_FULL_Ty, settings_sims, settings_input )
  ddf_obs_Ty <- ddf_obs_Ty %>% filter_days( settings_calib_FULL_Ty$filter_days, settings_calib_FULL_Ty$path_gepisat )
  save( ddf_obs_Ty, file = "data/ddf_obs_Ty.Rdata" )
} else {
  load("data/ddf_obs_Ty.Rdata")
}
print(paste0("Total number of calibration target data points: ", sum(!is.na(ddf_obs_Ty$gpp_obs))))

settings_calib_FULL_Ty <- calib_sofun(
  setup          = setup_sofun,
  settings_calib = settings_calib_FULL_Ty,
  settings_sims  = settings_sims,
  settings_input = settings_input,
  ddf_obs        = ddf_obs_Ty
  )
```

