---
title: "Annual mean GPP at FLUXNET evaluation"
author: "Beni"
date: "10/27/2020"
output: html_document
---

This is from the git repository *eval_pmodel* available [here](https://github.com/stineb/eval_pmodel).

Data loaded here (`~/eval_pmodel/calib_results/out_eval_FULL.Rdata`) is available on Euler at `~/data/stocker20gmd_outputs/rdata_objects/`.

```{r setup, include=FALSE}
library(tidyverse)
library(rsofun)
library(rbeni)
library(cowplot)

load("~/eval_pmodel/calib_results/out_eval_FULL.Rdata")
```

## Evaluation

This is the part of the evaluation from Stocker et al., 2020 GMD where annual mean GPP from P-model site-scale simulations are evaluated against observations from FLUXNET2015 sites.

The relevant data is in the list as follows:
```{r}
print(out_eval_FULL$gpp$fluxnet2015$data$meandf)
```

Site meta information, including geographical position, are available from the ingestr package (object `siteinfo_fluxnet2015`).
```{r}
library(ingestr)
siteinfo_fluxnet2015
```


## Visualisation

Using the data as shown above run this to reproduce Fig. XXX in Stocker et al., 2020 GMD.
```{r cars}
source("plot_modobs_spatial_annual2.R")

gg_FULL <- plot_modobs_spatial_annual2(out_eval_FULL)

gg_FULL +
  labs(title = "FULL", 
       y = expression( paste("observed GPP (gC m"^-2, "yr"^-1, ")" ) ), 
       x = expression( paste("simulated GPP (gC m"^-2, "yr"^-1, ")" ) )
      ) +
  xlim(0, 4000) + ylim(0, 4000)
```

