---
title: "LUE variations"
author: "Beni Stocker"
date: "5/10/2019"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyr)
library(rbeni)
library(RColorBrewer)
```

Evaluate light use efficiency.

## Daily
```{r}
showsites <- c("FR-Pue", "AU-How", "BE-Vie")
if (!exists("out_eval_ORG"))  load("./calib_results/out_eval_ORG.Rdata")
if (!exists("out_eval_FULL")) load("./calib_results/out_eval_FULL.Rdata")

load("~/eval_pmodel/data/obs_eval_NT_WITHFORCING.Rdata")

mc <- 12.0107  # molecular mass of carbon

ddf_FULL <- out_eval_FULL$gpp$fluxnet2015$data$ddf %>% 
  left_join(dplyr::select(obs_eval_NT$ddf, date, sitename, fapar, ppfd_fluxnet2015), by = c("sitename", "date")) %>% 
  mutate(ppfd_fluxnet2015 = myapprox(ppfd_fluxnet2015),
         fapar            = myapprox(fapar)) %>%
  mutate(apar = ppfd_fluxnet2015 * fapar) %>% 
  dplyr::filter(apar > 0.1) %>% 
  rename(gpp_obs = obs, gpp_mod = mod) %>% 
  mutate(lue_obs = gpp_obs / (mc * apar),
         lue_mod = gpp_mod / (mc * apar) ) %>% 
  mutate(lue_obs = remove_outliers(lue_obs),
         lue_mod = remove_outliers(lue_mod))

ddf_ORG <- out_eval_ORG$gpp$fluxnet2015$data$ddf %>% 
  left_join(dplyr::select(obs_eval_NT$ddf, date, sitename, fapar, ppfd_fluxnet2015), by = c("sitename", "date")) %>% 
  mutate(ppfd_fluxnet2015 = myapprox(ppfd_fluxnet2015),
         fapar            = myapprox(fapar)) %>%
  mutate(apar = ppfd_fluxnet2015 * fapar) %>% 
  dplyr::filter(apar > 0.1) %>% 
  rename(gpp_obs = obs, gpp_mod = mod) %>% 
  mutate(lue_obs = gpp_obs / (mc * apar),
         lue_mod = gpp_mod / (mc * apar) ) %>% 
  mutate(lue_obs = remove_outliers(lue_obs),
         lue_mod = remove_outliers(lue_mod))
```

Something is going odd. Check distribution of LUE values. 
```{r}
ddf_FULL %>% 
  drop_na(gpp_obs, gpp_mod) %>% 
  mutate(gpp_mod = gpp_mod * 1e3, gpp_obs = gpp_obs * 1e3) %>% 
  gather(modobs, gpp, c(gpp_obs, gpp_mod)) %>% 
  ggplot(aes(x = modobs, y=gpp, fill=modobs)) +
  geom_violin() +
  theme_classic() +
  scale_fill_brewer(palette="Paired", 
                    breaks=c("gpp_obs", "gpp_mod"), 
                    labels=c("Observed", "Modelled")) +
  labs(fill="", x="Vegetation type", y=expression(paste("gpp (mmol mol" ^{-1}, ")"))) + 
  theme(legend.position="top")

ddf_FULL %>% 
  drop_na(lue_obs, lue_mod) %>% 
  mutate(lue_mod = lue_mod * 1e3, lue_obs = lue_obs * 1e3) %>% 
  gather(modobs, lue, c(lue_obs, lue_mod)) %>% 
  ggplot(aes(x = modobs, y=lue, fill=modobs)) +
  geom_violin() +
  theme_classic() +
  scale_fill_brewer(palette="Paired", 
                    breaks=c("lue_obs", "lue_mod"), 
                    labels=c("Observed", "Modelled")) +
  labs(fill="", x="Vegetation type", y=expression(paste("LUE (mmol mol" ^{-1}, ")"))) + 
  theme(legend.position="top")


gg <- ddf_FULL %>% analyse_modobs2("lue_obs", "lue_mod", type = "heat")
gg
```


Compare coefficient of variations in LUE model.
```{r}
cv <- function(vec, ...){
  sd(vec, ...) / mean(vec, ...)
}
df_cv <- ddf_FULL %>% 
  summarise(gpp_obs = cv(gpp_obs, na.rm=TRUE),
            ppfd_fluxnet2015 = cv(ppfd_fluxnet2015, na.rm=TRUE),
            fapar = cv(fapar, na.rm=TRUE),
            lue_obs = cv(lue_obs, na.rm=TRUE))
print(df_cv)
```


## Monthly

```{r}
mdf_FULL <- ddf_FULL %>%
  mutate(moy = month(date), year = year(date)) %>% 
  group_by(sitename, year, moy) %>% 
  summarise(lue_obs = mean(lue_obs, na.rm=TRUE),
            lue_mod = mean(lue_mod, na.rm=TRUE)) %>% 
  right_join(dplyr::rename(out_eval_FULL$gpp$fluxnet2015$data$mdf, gpp_mod = mod, gpp_obs = obs), by = c("sitename", "year", "moy"))

mdf_ORG <- ddf_ORG %>%
  mutate(moy = month(date), year = year(date)) %>% 
  group_by(sitename, year, moy) %>% 
  summarise(lue_obs = mean(lue_obs, na.rm=TRUE),
            lue_mod = mean(lue_mod, na.rm=TRUE)) %>% 
  right_join(dplyr::rename(out_eval_ORG$gpp$fluxnet2015$data$mdf, gpp_mod = mod, gpp_obs = obs), by = c("sitename", "year", "moy"))

# FULL
out_mdf_FULL <- mdf_FULL %>% 
  ungroup %>% 
  drop_na(lue_obs, lue_mod) %>% 
  mutate(lue_mod = lue_mod * 1e3, lue_obs = lue_obs * 1e3) %>% 
  rbeni::analyse_modobs2("lue_mod", "lue_obs", type = "heat")

gg_modobs_mdf_FULL <- out_mdf_FULL$gg +
  labs(x = expression(paste("Modelled LUE (mmol mol" ^{-1}, ")")),
       y = expression(paste("Observed LUE (mmol mol" ^{-1}, ")")))
print(gg_modobs_mdf_FULL)

# ORG
out_mdf_ORG <- mdf_ORG %>% 
  ungroup %>% 
  drop_na(lue_obs, lue_mod) %>% 
  mutate(lue_mod = lue_mod * 1e3, lue_obs = lue_obs * 1e3) %>% 
  rbeni::analyse_modobs2("lue_mod", "lue_obs", type = "heat")

gg_modobs_mdf_ORG <- out_mdf_ORG$gg +
  labs(x = expression(paste("Modelled LUE (mmol mol" ^{-1}, ")")),
       y = expression(paste("Observed LUE (mmol mol" ^{-1}, ")")))
print(gg_modobs_mdf_ORG)
```

<!-- ## 8-daily -->

<!-- ```{r} -->
<!-- xdf <- out_eval_FULL$gpp$fluxnet2015$data$xdf -->

<!-- xdf <- ddf_FULL %>% -->
<!--   mutate(moy = month(date), year = year(date)) %>%  -->
<!--   group_by(sitename, year, moy) %>%  -->
<!--   summarise(lue_obs = mean(lue_obs, na.rm=TRUE), -->
<!--             lue_mod = mean(lue_mod, na.rm=TRUE)) %>%  -->
<!--   right_join(out_eval_FULL$gpp$fluxnet2015$data$xdf, by = c("sitename", "year", "moy")) -->

<!-- xdf %>%  -->
<!--   ungroup %>%  -->
<!--   drop_na(lue_obs, lue_mod) %>%  -->
<!--   mutate(lue_mod = lue_mod * 1e3, lue_obs = lue_obs * 1e3) %>%  -->
<!--   rbeni::analyse_modobs2("lue_mod", "lue_obs", type = "heat", filnam = "fig/modobs_lue_monthly.pdf", xlab = expression(paste("Modelled LUE (mmol mol" ^{-1}, ")")), ylab = expression(paste("Observed LUE (mmol mol" ^{-1}, ")"))) -->
<!-- ``` -->

## Mean seasonal cycle

```{r}
doydf_FULL <- ddf_FULL %>% 
  mutate(doy = yday(date)) %>% 
  group_by(sitename, doy) %>% 
  summarise(lue_obs = mean(lue_obs, na.rm = TRUE),
            lue_mod = mean(lue_mod, na.rm = TRUE)) %>% 
  ungroup()

doydf_FULL %>% 
  rbeni::analyse_modobs2(
    "lue_mod", "lue_obs", 
    xlab = expression(paste("Modelled LUE (mol mol" ^{-1}, ")")), 
    ylab = expression(paste("Observed LUE (mol mol" ^{-1}, ")")), type="heat")

doydf_ORG <- ddf_ORG %>% 
  mutate(doy = yday(date)) %>% 
  group_by(sitename, doy) %>% 
  summarise(lue_obs = mean(lue_obs, na.rm = TRUE),
            lue_mod = mean(lue_mod, na.rm = TRUE)) %>% 
  ungroup()

doydf_ORG %>% 
  rbeni::analyse_modobs2(
    "lue_mod", "lue_obs", 
    xlab = expression(paste("Modelled LUE (mol mol" ^{-1}, ")")), 
    ylab = expression(paste("Observed LUE (mol mol" ^{-1}, ")")), type="heat")
```

## Check time series for suspicious sites

```{r}
ddf_FULL %>%
  filter(sitename == "AR-SLu") %>% 
  ggplot() +
  geom_line(aes(x = date, y = lue_obs)) +
  geom_line(aes(x = date, y = lue_mod), col='red')

ddf_FULL %>%
  filter(sitename == "CH-Oe1") %>% 
  ggplot() +
  geom_line(aes(x = date, y = lue_obs)) +
  geom_line(aes(x = date, y = lue_mod), col='red')
```


## Annual

```{r}
## calculate annual LUE as annual total gpp devided by annual toal light ==> bad
adf_FULL <- ddf_FULL %>%
  mutate(year = year(date)) %>%
  group_by(sitename, year) %>%
  summarise( apar = sum(apar)) %>%
  dplyr::filter(apar > 0.1) %>%
  right_join(out_eval_FULL$gpp$fluxnet2015$data$adf, by=c("sitename", "year")) %>%
  rename(gpp_obs = obs, gpp_mod = mod) %>%
  mutate(lue_obs = gpp_obs / (mc * apar),
         lue_mod = gpp_mod / (mc * apar) ) %>%
  ungroup()  %>%
  left_join(rsofun::metainfo_Tier1_sites_kgclimate_fluxnet2015 %>% dplyr::select(sitename, classid),
            by="sitename") %>%
  mutate(lue_obs = remove_outliers(lue_obs),
         lue_mod = remove_outliers(lue_mod))

out_adf_FULL <- adf_FULL %>% rbeni::analyse_modobs2("lue_mod", "lue_obs", xlab = expression(paste("Modelled LUE (mol mol" ^{-1}, ")")), ylab = expression(paste("Observed LUE (mol mol" ^{-1}, ")")))
print(out_adf_FULL$gg)

## calculate annual LUE as annual total gpp devided by annual toal light ==> bad
adf_ORG <- ddf_ORG %>%
  mutate(year = year(date)) %>%
  group_by(sitename, year) %>%
  summarise( apar = sum(apar)) %>%
  dplyr::filter(apar > 0.1) %>%
  right_join(out_eval_ORG$gpp$fluxnet2015$data$adf, by=c("sitename", "year")) %>%
  rename(gpp_obs = obs, gpp_mod = mod) %>%
  mutate(lue_obs = gpp_obs / (mc * apar),
         lue_mod = gpp_mod / (mc * apar) ) %>%
  ungroup()  %>%
  left_join(rsofun::metainfo_Tier1_sites_kgclimate_fluxnet2015 %>% dplyr::select(sitename, classid),
            by="sitename") %>%
  mutate(lue_obs = remove_outliers(lue_obs),
         lue_mod = remove_outliers(lue_mod))

out_adf_ORG <- adf_ORG %>% rbeni::analyse_modobs2("lue_mod", "lue_obs", xlab = expression(paste("Modelled LUE (mol mol" ^{-1}, ")")), ylab = expression(paste("Observed LUE (mol mol" ^{-1}, ")")))
print(out_adf_ORG$gg)

# ## FULL: calculate annual LUE mean across daily LUE  ==> better? 
# adf_FULL <- ddf_FULL %>%   
#   mutate(year = year(date)) %>% 
#   group_by(sitename, year) %>% 
#   summarise( lue_obs = mean(lue_obs, na.rm = TRUE), lue_mod = mean(lue_mod, na.rm = TRUE)) %>% 
#   # right_join(out_eval_FULL$gpp$fluxnet2015$data$adf, by=c("sitename", "year")) %>%
#   ungroup()  %>%
#   left_join(rsofun::metainfo_Tier1_sites_kgclimate_fluxnet2015 %>% dplyr::select(sitename, classid),
#             by="sitename") %>% 
#   mutate(lue_obs = remove_outliers(lue_obs),
#          lue_mod = remove_outliers(lue_mod))
#   
# out_adf_FULL <- adf_FULL %>% rbeni::analyse_modobs2("lue_mod", "lue_obs", xlab = expression(paste("Modelled LUE (mol mol" ^{-1}, ")")), ylab = expression(paste("Observed LUE (mol mol" ^{-1}, ")")))
# out_adf_FULL$gg
# 
# ## ORG: calculate annual LUE mean across daily LUE  ==> better? 
# adf_ORG <- ddf_ORG %>%   
#   mutate(year = year(date)) %>% 
#   group_by(sitename, year) %>% 
#   summarise( lue_obs = mean(lue_obs, na.rm = TRUE), lue_mod = mean(lue_mod, na.rm = TRUE)) %>% 
#   ungroup()  %>%
#   left_join(rsofun::metainfo_Tier1_sites_kgclimate_fluxnet2015 %>% dplyr::select(sitename, classid),
#             by="sitename") %>% 
#   mutate(lue_obs = remove_outliers(lue_obs),
#          lue_mod = remove_outliers(lue_mod))
#   
# out_adf_ORG <- adf_ORG %>% rbeni::analyse_modobs2("lue_mod", "lue_obs", xlab = expression(paste("Modelled LUE (mol mol" ^{-1}, ")")), ylab = expression(paste("Observed LUE (mol mol" ^{-1}, ")")))
# out_adf_ORG$gg
```

## By site (spatial) and veg type

```{r}
## mean by site
df_FULL <- adf_FULL %>% 
  group_by(sitename) %>% 
  summarise(lue_obs = mean(lue_obs, na.rm = TRUE),
            lue_mod = mean(lue_mod, na.rm = TRUE)) %>% 
  left_join(rsofun::metainfo_Tier1_sites_kgclimate_fluxnet2015 %>% dplyr::select(sitename, classid), 
            by="sitename") %>% 
  drop_na(lue_obs, lue_mod) %>% 
  mutate(lue_mod = lue_mod * 1e3, lue_obs = lue_obs * 1e3)

df_ORG <- adf_ORG %>% 
  group_by(sitename) %>% 
  summarise(lue_obs = mean(lue_obs, na.rm = TRUE),
            lue_mod = mean(lue_mod, na.rm = TRUE)) %>% 
  left_join(rsofun::metainfo_Tier1_sites_kgclimate_fluxnet2015 %>% dplyr::select(sitename, classid), 
            by="sitename") %>% 
  drop_na(lue_obs, lue_mod) %>% 
  mutate(lue_mod = lue_mod * 1e3, lue_obs = lue_obs * 1e3)

## mean by vegetation type
vegdf_FULL <- df_FULL %>% 
  ungroup() %>% 
  group_by(classid) %>% 
  summarise(lue_obs = mean(lue_obs, na.rm = TRUE),
            lue_mod = mean(lue_mod, na.rm = TRUE))

vegdf_ORG <- df_ORG %>% 
  ungroup() %>% 
  group_by(classid) %>% 
  summarise(lue_obs = mean(lue_obs, na.rm = TRUE),
            lue_mod = mean(lue_mod, na.rm = TRUE))


##################
# FULL setup
##################
out_df_FULL <- df_FULL %>% 
  rbeni::analyse_modobs2("lue_mod", "lue_obs", xlab="Modelled LUE", ylab="Observed LUE") # , filnam = "fig/modobs_lue_bysite.pdf"

rsq_lab <- format( out_df_FULL$df_metrics %>% dplyr::filter(.metric=="rsq") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 2 )
rmse_lab <- format( out_df_FULL$df_metrics %>% dplyr::filter(.metric=="rmse") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 3 )
bias_lab <- format( out_df_FULL$df_metrics %>% dplyr::filter(.metric=="bias") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 3 )
slope_lab <- format( out_df_FULL$df_metrics %>% dplyr::filter(.metric=="slope") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 3 )
n_lab <- format( out_df_FULL$df_metrics %>% dplyr::filter(.metric=="n") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 3 )

out_vegdf_FULL <- vegdf_FULL %>% 
  rbeni::analyse_modobs2("lue_mod", "lue_obs", xlab="Modelled LUE", ylab="Observed LUE")

rsq_lab2 <- format( out_vegdf_FULL$df_metrics %>% dplyr::filter(.metric=="rsq") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 2 )
rmse_lab2 <- format( out_vegdf_FULL$df_metrics %>% dplyr::filter(.metric=="rmse") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 3 )
bias_lab2 <- format( out_vegdf_FULL$df_metrics %>% dplyr::filter(.metric=="bias") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 3 )
slope_lab2 <- format( out_vegdf_FULL$df_metrics %>% dplyr::filter(.metric=="slope") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 3 )
n_lab2 <- format( out_vegdf_FULL$df_metrics %>% dplyr::filter(.metric=="n") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 3 )

## scatterplot
gg_lue_spatial_FULL <- ggplot() +
  geom_point(data=df_FULL, aes(x=lue_mod, y=lue_obs, color=classid), size=1.5) +
  geom_point(data=vegdf_FULL, aes(x=lue_mod, y=lue_obs, color=classid), size=5) +
  geom_smooth(data=df_FULL, aes(x=lue_mod, y=lue_obs), method = "lm", color="red", size=0.5) +
  geom_abline(intercept=0, slope=1, linetype="dotted") +
  theme_classic() +
  scale_color_brewer(palette="Paired") +
  labs(
        subtitle = bquote(
          # atop(
            # "Sites:" ~
            italic(R)^2 == .(rsq_lab) ~ (.(rsq_lab2)) ~~~
            # RMSE == .(rmse_lab) ~~~
            # bias == .(bias_lab) ~~~
            slope == .(slope_lab) ~ (.(slope_lab2)) ~~~
            italic(N) == .(n_lab) ~ (.(n_lab2))
          # , 
          # "Vegetation types:" ~
          # italic(R)^2 == .(rsq_lab2) ~~~
          # RMSE == .(rmse_lab2) ~~~
          # bias == .(bias_lab2) ~~~
          # slope == .(slope_lab2) ~~~
          # italic(N) == .(n_lab2) 
        # )
         ),
        x = expression(paste("Modelled LUE (mmol mol" ^{-1}, ")")), 
        y = expression(paste("Observed LUE (mmol mol" ^{-1}, ")")),
        color="")
print(gg_lue_spatial_FULL)

# xxxxxx take this
ggsave("fig/modobs_lue_bysite_classid_FULL.pdf", width=5, height=5)


##################
# ORG setup
##################
out_df_ORG <- df_ORG %>% 
  # dplyr::filter(classid != "OSH") %>% 
  rbeni::analyse_modobs2("lue_mod", "lue_obs", xlab="Modelled LUE", ylab="Observed LUE")

rsq_lab <- format( out_df_ORG$df_metrics %>% dplyr::filter(.metric=="rsq") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 2 )
rmse_lab <- format( out_df_ORG$df_metrics %>% dplyr::filter(.metric=="rmse") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 3 )
bias_lab <- format( out_df_ORG$df_metrics %>% dplyr::filter(.metric=="bias") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 3 )
slope_lab <- format( out_df_ORG$df_metrics %>% dplyr::filter(.metric=="slope") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 3 )
n_lab <- format( out_df_ORG$df_metrics %>% dplyr::filter(.metric=="n") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 3 )

out_vegdf_ORG <- vegdf_ORG %>% 
  dplyr::filter(classid != "OSH") %>% 
  rbeni::analyse_modobs2("lue_mod", "lue_obs", xlab="Modelled LUE", ylab="Observed LUE") # , filnam = 

rsq_lab2 <- format( out_vegdf_ORG$df_metrics %>% dplyr::filter(.metric=="rsq") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 2 )
rmse_lab2 <- format( out_vegdf_ORG$df_metrics %>% dplyr::filter(.metric=="rmse") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 3 )
bias_lab2 <- format( out_vegdf_ORG$df_metrics %>% dplyr::filter(.metric=="bias") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 3 )
slope_lab2 <- format( out_vegdf_ORG$df_metrics %>% dplyr::filter(.metric=="slope") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 3 )
n_lab2 <- format( out_vegdf_ORG$df_metrics %>% dplyr::filter(.metric=="n") %>% dplyr::select(.estimate) %>% unlist() %>% unname(), digits = 3 )

gg_lue_spatial_ORG <- ggplot() +
  geom_point(data=df_ORG, aes(x=lue_mod, y=lue_obs, color=classid), size=1.5) +
  geom_point(data=vegdf_ORG, aes(x=lue_mod, y=lue_obs, color=classid), size=5) +
  geom_smooth(data=df_ORG, aes(x=lue_mod, y=lue_obs), method = "lm", color="red", size=0.5) +
  geom_abline(intercept=0, slope=1, linetype="dotted") +
  theme_classic() +
  scale_color_brewer(palette="Paired") +
  labs(
        subtitle = bquote(
          # atop(
            # "Sites:" ~
            italic(R)^2 == .(rsq_lab) ~ (.(rsq_lab2)) ~~~
            # RMSE == .(rmse_lab) ~~~
            # bias == .(bias_lab) ~~~
            slope == .(slope_lab) ~ (.(slope_lab2)) ~~~
            italic(N) == .(n_lab) ~ (.(n_lab2))
          # , 
          # "Vegetation types:" ~
          # italic(R)^2 == .(rsq_lab2) ~~~
          # RMSE == .(rmse_lab2) ~~~
          # bias == .(bias_lab2) ~~~
          # slope == .(slope_lab2) ~~~
          # italic(N) == .(n_lab2) 
        # )
         ),
        x = expression(paste("Modelled LUE (mmol mol" ^{-1}, ")")), 
        y = expression(paste("Observed LUE (mmol mol" ^{-1}, ")")),
        color="")
print(gg_lue_spatial_ORG)

# xxxxxx take this
ggsave("fig/modobs_lue_bysite_classid_ORG.pdf", width=5, height=5)


## boxplot 
gg_FULL <- df_FULL %>% 
  drop_na(lue_obs, lue_mod) %>% 
  mutate(lue_mod = lue_mod * 1e3, lue_obs = lue_obs * 1e3) %>% 
  gather(modobs, lue, c(lue_obs, lue_mod)) %>% 
  ggplot(aes(x=classid, y=lue, fill=modobs)) +
  geom_boxplot() +
  theme_classic() +
  scale_fill_brewer(palette="Paired", 
                    breaks=c("lue_obs", "lue_mod"), 
                    labels=c("Observed", "Modelled")) +
  labs(fill="", x="Vegetation type", y=expression(paste("LUE (mmol mol" ^{-1}, ")"))) + 
  theme(legend.position="top")
print(gg_FULL)
ggsave("fig/boxplot_lue_bysite_classid_FULL.pdf", width=5, height=5)

gg_ORG <- df_ORG %>% 
  drop_na(lue_obs, lue_mod) %>% 
  mutate(lue_mod = lue_mod * 1e3, lue_obs = lue_obs * 1e3) %>% 
  gather(modobs, lue, c(lue_obs, lue_mod)) %>% 
  ggplot(aes(x=classid, y=lue, fill=modobs)) +
  geom_boxplot() +
  theme_classic() +
  scale_fill_brewer(palette="Paired", 
                    breaks=c("lue_obs", "lue_mod"), 
                    labels=c("Observed", "Modelled")) +
  labs(fill="", x="Vegetation type", y=expression(paste("LUE (mmol mol" ^{-1}, ")"))) + 
  theme(legend.position="top")
print(gg_ORG)
ggsave("fig/boxplot_lue_bysite_classid_ORG.pdf", width=5, height=5)
```

<!-- ## By vegetation type -->

<!-- ```{r} -->

<!-- vegdf_FULL %>%  -->
<!--   mutate(lue_mod = lue_mod * 1e3, lue_obs = lue_obs * 1e3) %>%  -->
<!--   rbeni::analyse_modobs2("lue_mod", "lue_obs") -->


<!-- ggplot(aes(x=lue_mod, y=lue_obs)) + -->
<!--   geom_point(size=1.5) + -->
<!--   geom_smooth(method = "lm", color="red", size=0.5) + -->
<!--   geom_abline(intercept=0, slope=1, linetype="dotted") + -->
<!--   # coord_fixed() + -->
<!--   theme_classic() + -->
<!--   scale_color_brewer(palette="Paired") -->


<!-- ``` -->

## Re-calculating

Can this really be the case: Predicted LUE has has explanatory power, yet, when using a fixed uniform LUE value, we don't add explanatory power to predicted GPP?


### LUE

LUE as simulated by the P-model, daily values (sampling only 10% of the data here to keep it light). Observed LUE is calculated as `gpp_obs / (fapar * ppfd)`. 

$$
\text{LUE}_\text{obs} = \frac{\text{GPP}_\text{obs}}{\text{fAPAR} \cdot \text{PPFD}}
$$

```{r}
load("./calib_results/linmod_NULL.RData")
lue_fit <- coef(linmod)
load("calib_results/out_eval_NULL.Rdata")

ddf_FULL_test <- ddf_FULL %>% 
  sample_frac(0.1) %>% 
  mutate(gpp_mod_reNULL = lue_fit * fapar * ppfd_fluxnet2015) %>% 
  left_join( select(out_eval_NULL$gpp$fluxnet2015$data$ddf, sitename, date, gpp_mod_NULL = gpp_mod), by = c("sitename", "date")) %>% 
  tidyr::drop_na(lue_mod, lue_obs, gpp_mod_NULL, gpp_mod_reNULL)

ddf_FULL_test %>% rbeni::analyse_modobs2("lue_mod", "lue_obs", xlab="Modelled LUE", ylab="Observed LUE", type="heat")
```

### GPP

GPP predicted using P-model-simulated LUE and the same PPFD and fAPAR as used to calculate observed LUE above.
```{r}
ddf_FULL_test %>% rbeni::analyse_modobs2("gpp_mod", "gpp_obs", xlab="Modelled LUE", ylab="Observed LUE", type="heat")
```

Compare this to the GPP re-calculated using a fixed and uniform LUE value fitted to the data as done for the NULL model described in the manuscript.

```{r}
ddf_FULL_test %>% rbeni::analyse_modobs2("gpp_mod_reNULL", "gpp_obs", xlab="Modelled GPP", ylab="Observed GPP", type="heat")
```

And now compare this to the exact same data I was using for benchmarking before (NULL).
```{r}
ddf_FULL_test %>% rbeni::analyse_modobs2("gpp_mod_NULL", "gpp_obs", xlab="Modelled GPP", ylab="Observed GPP", type="heat")
```


## Publication figure

```{r}
library(cowplot)
plot_grid(gg_modobs_mdf_FULL, gg_lue_spatial_FULL, labels = "auto", label_size = 12, rel_widths = c(1, 1.1))
ggsave("fig/modobs_lue_FULL.pdf", width=10, height=5)  

plot_grid(gg_modobs_mdf_ORG, gg_lue_spatial_ORG, labels = "auto", label_size = 12, rel_widths = c(1, 1.1))
ggsave("fig/modobs_lue_ORG.pdf", width=10, height=5)  
```